The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-09 Article/Article20140406Granada/LatexArt/article_main.tex
Matlab-Metatrader comparision, Figures

It was also decided to test the effectiveness of the algorithm in terms of one candle 1h. The results are shown in Table \ref{tab:tab3} and Table \ref{tab:tab4}.

\begin{table}[h!]
\centering
\caption{PerCandle EURUSD.}
\label{tab:tab3}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning\textbackslash Test &	8	 &	10 &		15	 &	20\\ \hline
40 &		-2.207E-06 &		-6.443E-06 &		-1.219E-05 &		-5.641E-06\\ \hline
60 &		3.695E-07 &		-1.327E-06 &		2.358E-06 &		1.425E-05\\ \hline
80 &		-1.989E-06 &		8.427E-06	 &	\textbf{2.062E-05} &		5.3549E-06\\ \hline
100	 &	2.465E-06 &		4.517E-06 &		-8.981E-07 &		1.571E-07\\ \hline
\end{tabular}
\end{table}
\FloatBarrier

\begin{table}[h!]
\centering
\caption{PerCandle GBPUSD.}
\label{tab:tab4}
\begin{tabular}{|l|r|r|r|r|} \hline
Learning\textbackslash Test &	8	 & 	10 &		15	 &	20\\ \hline
40	 & -2.949E-05 & 	1.457E-06 & 	-2.768E-05	 & -1.578E-05\\ \hline
60	 & -2.289E-05 & 	-2.912E-05 & 	-1.250E-06 & 	-1.162E-05\\ \hline
80	 & -3.043E-06 & 	-2.408E-05	 & \textbf{1.551E-05} & 	-1.780E-05\\ \hline
100	 & -1.299E-05 & 	-1.228E-05 & 	-3.110E-06	 & -2.143E-05\\ \hline
\end{tabular}
\end{table}
\FloatBarrier

@@

In addition, effectiveness studies were carried out and optimized for different test periods. To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles. 
Figure \ref{fig:fig10} and Figure \ref{fig:fig11} present the results.

@@

Below are presented balance comparisons in Matlab and MetaTrader environments:
\begin{enumerate}
\item for GBPUSD currency pair using 1h candles values in time period of 2013.01.09 - 2013.12.30 in two different approches:
\begin{itemize}
\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig10} and Figure \ref{fig:fig11}). Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig12} and Figure \ref{fig:fig13})
\end{itemize}
In both approaches following assumptions were done:
\begin{itemize}
\item spread was 0.00028, 
\item initial deposit was 50000 EUR,
\item size of the opening positions was 1 lot,
\item each testing period lasted 15 candles.
\end{itemize}
\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approches:
\begin{itemize}
\item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig14} and Figure \ref{fig:fig15}) Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig16} and Figure \ref{fig:fig17})
\end{itemize}
In both approaches following assumptions were done:
\begin{itemize}
\item spread was 0.00016, 
\item initial deposit was 10000 EUR,
\item size of the opening positions was 1 lot,
\item each testing period lasted 15 candles.
\end{itemize}
\end{enumerate}

>>>>

@@

In addition, effectiveness studies were carried out and optimized for different test periods. To these results can be compared with each other, has been carried out their link, and the results were divided by the length of the test period, expressed by the number of candles. 
Figure \ref{fig:fig10} present the results for EURUSD currency pair.

@@

Below are presented balance comparisons in Matlab and MetaTrader environments:
\begin{enumerate}
\item for EURUSD currency pair using 1h candles values in time period of 2012.01.20 - 2013.01.01 in two different approches:
\begin{itemize}
\item with fixed parameters: $p1$=34, $p2$=4, $p3$=3, $p4$=-0.0060, $p5$=0.0060. Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader 
\end{itemize}
In both approaches following assumptions were done:
\begin{itemize}
\item spread was 0.00016, 
\item initial deposit was 10000 EUR,
\item size of the opening positions was 1 lot,
\item each testing period lasted 15 candles.
\end{itemize}
\item for GBPUSD currency pair using 1h candles values in time period of 2013.01.09 - 2013.12.30 in two different approches:
\begin{itemize}
\item with fixed parameters: $p1$=27, $p2$=4, $p3$=1, $p4$=-0.0060, $p5$=0.0060 (Figure \ref{fig:fig12} and Figure \ref{fig:fig13}). Optimal parameters in that case were computed in Matlab for the first testing period and then were used for all testing periods.
\item with dynamic parameters that were changed every testing period, regarding to their values computed in Matlab that were put to MetaTrader (Figure \ref{fig:fig14} and Figure \ref{fig:fig13})
\end{itemize}
In both approaches following assumptions were done:
\begin{itemize}
\item spread was 0.00028, 
\item initial deposit was 50000 EUR,
\item size of the opening positions was 1 lot,
\item each testing period lasted 15 candles.
\end{itemize}
\end{enumerate}
